---
title: "AdultRegionInfo"
author: "Yu-Kuan, Pan"
date: "2023-03-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(Seurat)
library(ape)
library(Matrix)
#library(tidyverse)
library(dplyr)
library(openxlsx)
```

```{r}
load("./hipSubS4objCluster.rda")
load("./regionData.rda")
```

```{r}
Idents(region.data)<- region.data@meta.data$region_label
region.data<-BuildClusterTree(region.data,
                               features=rownames(region.data))
PlotClusterTree(region.data)

```

```{r}
region.data@meta.data<-mutate(region.data@meta.data,
                              region="NEO")
```

```{r}
for(i in 1:nrow(region.data@meta.data)){
  if(region.data@meta.data$region_label[i]=="HIP"){
    region.data@meta.data$region[i]="HIP"
  }
  else if(region.data@meta.data$region_label[i]=="SUB-ProS"){
    region.data@meta.data$region[i]="SUB-ProS"
  }
  else if(region.data@meta.data$region_label[i]=="ENTm"){
    region.data@meta.data$region[i]="ENT"
  }
  else if(region.data@meta.data$region_label[i]=="ENTl"){
    region.data@meta.data$region[i]="ENT"
  }
}
```

```{r}
Idents(region.data)<-region.data@meta.data$region
```

```{r}
region.genelist<-FindAllMarkers(region.data)
```

```{r}
#region.genelist %>%
#  group_by(cluster) %>%
#  top_n(n=10,wt=avg_log2FC) -> top10
#DoHeatmap(region.data,features = top10$gene)
```

```{r}
#top10
```
## Hippocampus test 
```{r}
#for(i in 11:20){
#  print(VlnPlot(region.data, features = top10$gene[i], group.by = "region"))
#}
```

```{r}
FindMarkers(region.data, ident.1 = "HIP",
            min.diff.pct = 0.2, logfc.threshold = 0.5,
            only.pos = T) -> HIPDiff02FC07
```

```{r}
HIPDiff02FC07 %>%
  mutate(gene = rownames(HIPDiff02FC07)) -> HIPDiff02FC07
HIPDiff02FC07 
```


```{r}
for(i in 1:nrow(HIPDiff02FC07)){
  print(VlnPlot(region.data,
                features = rownames(HIPDiff02FC07)[i],
                group.by = "region"))
}
```

```{r}
HIPseq<- c(1, 4, 5, 10, 13)
#DimPlot(region.data, reduction = "umap")
FeaturePlot(region.data, features = "Zbtb20")
#for(i in 1:length(HIPseq)){
#  print(FeaturePlot(region.data, features = #HIPDiff02FC07$gene[HIPseq[i]]))
#}
```


## ENT test 
```{r}
FindMarkers(region.data, ident.1 = "ENT",
            min.diff.pct = 0.2, logfc.threshold = 0.5,
            only.pos = T) -> ENTDiff02FC05
```

```{r}
ENTDiff02FC05 %>% 
  mutate(gene = rownames(ENTDiff02FC05)) -> ENTDiff02FC05
ENTDiff02FC05
```


```{r}
for( i in 1:nrow(ENTDiff02FC05)){
  print(VlnPlot(region.data,
                features = rownames(ENTDiff02FC05)[i],
                group.by = "region"))
}
```

```{r}
#DimPlot(region.data, reduction = "umap", group.by = "region_label")
#ENTseq<- c(3, 4)
#for(i in 1:length(ENTseq)){
#  print(FeaturePlot(region.data, features = ENTDiff02FC05$gene[ENTseq[i]]))
#}
FeaturePlot(region.data, features = "Rxfp1")
```

## NEO test
```{r}
FindMarkers(region.data, ident.1 = "NEO",
            min.diff.pct = 0.2, logfc.threshold = 0.5,
            only.pos = T) -> NEODiff02FC07
```

```{r}
NEODiff02FC07 %>%
  mutate(gene = rownames(NEODiff02FC07)) -> NEODiff02FC07
NEODiff02FC07
```


```{r}
for( i in 1:nrow(NEODiff02FC07)){
  print(VlnPlot(region.data,
                features = rownames(NEODiff02FC07)[i],
                group.by = "region"))
}
```

```{r}
#DimPlot(region.data)
#NEOseq<- c(1, 3, 4, 5, 7, 9)
#DimPlot(region.data, reduction = "umap")
#for(i in 1:length(NEOseq)){
#  print(FeaturePlot(region.data, features = #NEODiff02FC07$gene[NEOseq[i]]))
#}
FeaturePlot(region.data, features = "S100a10")
```

## filter hippocampus information 
filter hippocampus information make sure sub-Prox is not included
```{r}
HipSub.s4obj.cluster@meta.data$seurat_clusters<- 
  HipSub.s4obj.cluster@active.ident
```

## generate area information 
generate information that classify dorsal and ventral 
based on clustered sub-regions within hippocmpus 
we combine dorsal DG, CA1 and CA3 and defined as dorsal hippocampus 
and the same process with the ventral part 
```{r}
HIPList<- WhichCells(HipSub.s4obj.cluster,
                     idents = c("DGd", "DGv", "CA1d", "CA1v", "CA3d", "CA3v"))
Hip.s4obj.cluster<- HipSub.s4obj.cluster[, HIPList]
```

```{r}
Hip.s4obj.cluster@meta.data %>% 
  mutate(area = ifelse(seurat_clusters == "DGd" | seurat_clusters == "CA1d" | seurat_clusters == "CA3d", "Dorsal", 
                       ifelse(seurat_clusters == "DGv" | seurat_clusters == "CA1v" | seurat_clusters == "CA3v", "Ventral", NA))) -> Hip.s4obj.cluster@meta.data
```

##HIP dorsal 
```{r}
FindMarkers(Hip.s4obj.cluster,
            ident.1 = "Dorsal",
            ident.2 = "Ventral",
            #logfc.threshold =  0.6, 
            #min.diff.pct = 0.13,
            logfc.threshold = 0.5,
            min.diff.pct = 0.2,
            group.by = "area",
            only.pos = T)-> HIPDDiff02Fc07
```

```{r}
HIPDDiff02Fc07 %>%
  mutate(gene = rownames(HIPDDiff02Fc07)) -> HIPDDiff02Fc07
HIPDDiff02Fc07
```

```{r}
for(i in 1:nrow(HIPDDiff02Fc07)){
  print(VlnPlot(Hip.s4obj.cluster,
                rownames(HIPDDiff02Fc07)[i],
                group.by = "area"))
}
```

```{r}
for(i in 1:nrow(HIPDDiff02Fc07)){
  print(VlnPlot(Hip.s4obj.cluster,
                rownames(HIPDDiff02Fc07)[i],
                group.by = "seurat_clusters"))
}
```


```{r}
DimPlot(region.data, reduction = "umap")
DimPlot(Hip.s4obj.cluster, reduction = "umap")
for(i in 1:nrow(HIPDDiff02Fc07)){
  print(FeaturePlot(region.data, features = HIPDDiff02Fc07$gene[i]))
  print(FeaturePlot(Hip.s4obj.cluster, features = HIPDDiff02Fc07$gene[i]))
}
```

```{r}
DimPlot(region.data, reduction = "umap", cols = c("#00BFC4",
                                                  "#7CAE00",
                                                  "#F8766D",
                                                  "#C77CFF"))
DimPlot(Hip.s4obj.cluster, reduction = "umap")
FeaturePlot(region.data, features = "Tdo2")
FeaturePlot(Hip.s4obj.cluster, features = "Tdo2")
```


## HIP ventral 
```{r}
FindMarkers(Hip.s4obj.cluster,
            ident.1 = "Ventral",
            ident.2 = "Dorsal",
            #logfc.threshold = 0.6,
            #min.diff.pct = 0.13,
            logfc.threshold = 0.5,
            min.diff.pct = 0.2,
            group.by = "area", 
            only.pos = T) -> HIPVDiff02Fc07
```

```{r}
HIPVDiff02Fc07 %>% 
  mutate(gene = rownames(HIPVDiff02Fc07)) -> HIPVDiff02Fc07
HIPVDiff02Fc07
```

```{r}
for(i in 1:nrow(HIPVDiff02Fc07)){
  print(VlnPlot(Hip.s4obj.cluster,
                features = rownames(HIPVDiff02Fc07)[i], 
                group.by = "area"))
}
```

```{r}
#DimPlot(region.data, reduction = "umap")
#DimPlot(Hip.s4obj.cluster, reduction = "umap")
FeaturePlot(region.data, features = "Dcn")
FeaturePlot(Hip.s4obj.cluster, features = "Dcn")
```

## HIP sub-region area test 
test out the 3 sub region within hippocampus (CA1, CA3, DG)
and compare each dorsal or ventral part with others to find 
each marker genes 

```{r}
FindAllMarkers(Hip.s4obj.cluster,
               logfc.threshold = 0.5,
               #min.diff.pct = 0.3,
               min.diff.pct = 0.2,
               only.pos = T) -> HIPsubDV
HIPsubDV
```

```{r}
HIPsubDV %>% 
  group_by(cluster) %>% 
  top_n(n = 10, wt = avg_log2FC) -> HIPsubDVTop10
HIPsubDVTop10
```

## DGd 
```{r}
for(i in 1:10){
  print(VlnPlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[i]))
}
```

```{r}
#none update
DGdseq<- c(4)
DimPlot(Hip.s4obj.cluster, reduction = "umap")
#for(i in 1:length(DGdseq)){
#  print(FeaturePlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[DGdseq[i]]))
#}
FeaturePlot(Hip.s4obj.cluster, features = "Tdo2")
```

```{r}
DGd<- FindMarkers(Hip.s4obj.cluster, ident.1 = "DGd", 
                  ident.2 = "DGv", logfc.threshold = 0.5, 
                  min.diff.pct = 0.2, only.pos = T)
DGd
```

```{r}
for(i in 1:nrow(DGd)){
  print(VlnPlot(Hip.s4obj.cluster, features = rownames(DGd)[i]))
}
```


## DGv
```{r}
for(i in 11:20){
  print(VlnPlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[i]))
}
```

```{r}
#none update
DGvSeq<- c(16)
for(i in 1:length(DGvSeq)){
  print(FeaturePlot(Hip.s4obj.cluster, features = HIPsubDVTop10$gene[DGvSeq[i]]))
}
```

```{r}
DGv<- FindMarkers(Hip.s4obj.cluster, ident.1 = "DGv", 
                  ident.2 = "DGd", logfc.threshold = 0.5, 
                  min.diff.pct = 0.2, only.pos = T)
DGv
```

```{r}
for(i in 1:nrow(DGv)){
  print(VlnPlot(Hip.s4obj.cluster, features = rownames(DGv)[i]))
}
```

## CA1v
```{r}
for(i in 21:30){
  print(VlnPlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[i]))
}
```

```{r}

#seqCA1v <- c(21, 22, 23, 24, 25, 26, 28)
#DimPlot(Hip.s4obj.cluster, reduction = "umap")
#for(i in 1:length(seqCA1v)){
#  print(FeaturePlot(Hip.s4obj.cluster,
#                    features = HIPsubDVTop10$gene[seqCA1v[i]]))
#}
FeaturePlot(Hip.s4obj.cluster, features = "Fibcd1")
```


## CA1d
```{r}
for(i in 31:40){
  print(VlnPlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[i]))
}
```

```{r}
#none update 
CA1dSeq<- c(31, 32, 33, 35, 36, 37, 39)
DimPlot(Hip.s4obj.cluster, reduction = "umap")
for(i in 1:length(CA1dSeq)){
  print(FeaturePlot(Hip.s4obj.cluster, features = HIPsubDVTop10$gene[CA1dSeq[i]]))
}
```

```{r}
FeaturePlot(Hip.s4obj.cluster, features = "Neurod6")
```


## CA3d
```{r}
for(i in 41:50){
  print(VlnPlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[i]))
}
```

```{r}
#none update
CA3dSeq<- c(41, 42, 44)
DimPlot(Hip.s4obj.cluster, reduction = "umap")
for(i in 1:length(CA3dSeq)){
  print(FeaturePlot(Hip.s4obj.cluster, features = HIPsubDVTop10$gene[CA3dSeq[i]]))
}

```

```{r}
FeaturePlot(Hip.s4obj.cluster, features = "Nrip3")
```


## CA3v 
```{r}
for(i in 51:60){
  print(VlnPlot(Hip.s4obj.cluster, HIPsubDVTop10$gene[i]))
}
```

```{r}
#none update

CA3VSeq<- c(52, 54, 56, 57, 60)
DimPlot(Hip.s4obj.cluster, reduction = "umap")
for(i in 1:length(CA3VSeq)){
  print(FeaturePlot(Hip.s4obj.cluster, features = HIPsubDVTop10$gene[CA3VSeq[i]]))
}
```


## ENT 
```{r}
ENT.s4obj<- region.data[, WhichCells(region.data, idents = "ENT")]
```

```{r}
DimPlot(ENT.s4obj, group.by = "region_label")
```

```{r}
ENTMec<- FindMarkers(ENT.s4obj,
                     ident.1 = "ENTm",
                     ident.2 = "ENTl",
                     min.diff.pct = 0.2,
                     logfc.threshold = 0.5,
                     #logfc.threshold = 0.5,
                     group.by = "region_label", 
                     only.pos = T)
```

```{r}
ENTMec %>%
  mutate(gene = rownames(ENTMec))
ENTMec
```


```{r}
for(i in 1:nrow(ENTMec)){
  print(VlnPlot(ENT.s4obj, features = rownames(ENTMec)[i],
                group.by = "region_label"))
}
```

```{r}
ENTmseq<- c(1, 2)
DimPlot(ENT.s4obj, reduction = "umap", group.by = "region_label")
for(i in 1:length(ENTmseq)){
  print(FeaturePlot(ENT.s4obj, features = rownames(ENTMec)[ENTmseq[i]]))
}
```


```{r}
ENTLec<- FindMarkers(ENT.s4obj,
                     ident.1 = "ENTl", 
                     ident.2 = "ENTm",
                     min.diff.pct = 0.2, 
                     logfc.threshold = 0.5,
                     #logfc.threshold = 0.4,
                     group.by = "region_label", 
                     only.pos = T)
```

```{r}
ENTLec %>%
  mutate(gene = rownames(ENTLec)) -> ENTLec
ENTLec
```


```{r}
for(i in 1: nrow(ENTLec)){
  print(VlnPlot(ENT.s4obj, features = rownames(ENTLec)[i], 
                group.by = "region_label"))
}
```

```{r}
DimPlot(ENT.s4obj, reduction = "umap", group.by = "region_label")
for(i in 1: nrow(ENTLec)){
  print(FeaturePlot(ENT.s4obj, features = rownames(ENTLec)[i]))
}
```

## cluster ENT information 
```{r}
ENT.s4obj<- region.data[, WhichCells(region.data, idents = "ENT")]
ENT.s4obj<- FindNeighbors(ENT.s4obj, dims = 1:10)
ENT.s4obj<- FindClusters(ENT.s4obj, resolution = 1.5)
ENT.s4obj<- RunUMAP(ENT.s4obj, dims = 1:10)
ENT.s4obj<- RunTSNE(ENT.s4obj, dims = 1:10)
```

```{r}
DimPlot(ENT.s4obj, reduction = "umap", group.by = "region_label")
```

## find marker genes at each cluster 
```{r}
FindAllMarkers(ENT.s4obj, logfc.threshold = 0.5,
               min.diff.pct = 0.2, only.pos = T)-> ENT.markers
ENT.markers
```

```{r}
ENT.markers %>%
  group_by(cluster) %>% 
  top_n(n= 10, wt = avg_log2FC) -> ENT.markers.top10
ENT.markers.top10
```


##MEC information
```{r}
ENTmseq<- c(1, 2)
DimPlot(ENT.s4obj, reduction = "umap", group.by = "region_label")
for(i in 1:length(ENTmseq)){
  print(FeaturePlot(ENT.s4obj, features = rownames(ENTMec)[ENTmseq[i]]))
}
```

##LEC information
```{r}
DimPlot(ENT.s4obj, reduction = "umap", group.by = "region_label")
for(i in 1: nrow(ENTLec)){
  print(FeaturePlot(ENT.s4obj, features = rownames(ENTLec)[i]))
}
```

##check layer2 Reelin and cabindin at Entorhinal 
```{r}
FeaturePlot(ENT.s4obj, features = "Wfs1", label = T) #layer2
FeaturePlot(ENT.s4obj, features = "Tbr1", label = T) # deep
FeaturePlot(ENT.s4obj, features = "Reln", label = T) #layer2 Reln
FeaturePlot(ENT.s4obj, features = "Calb1", label = T) # layer2 calbin1
```

# find unique cell from L2 Reln and Calb1
```{r}
length(setdiff(WhichCells(ENT.s4obj, expression = Reln>0),
               WhichCells(ENT.s4obj, expression = Calb1 >0)))
```

## differential expression 
```{r}
#Reln top
FindMarkers(ENT.s4obj, ident.1 = "3",
            min.diff.pct = 0.2, logfc.threshold = 0.5, 
            only.pos = T)
```

## L2 Reln
```{r}
VlnPlot(ENT.s4obj, features = "Reln")
FeaturePlot(ENT.s4obj, features = "Reln", label = T)
```

```{r}
# Reln 2nd
FindMarkers(ENT.s4obj, ident.1 = "10", 
            min.diff.pct = 0.2, logfc.threshold = 0.5, 
            only.pos = T)
```

```{r}
#Reln 3rd
FindMarkers(ENT.s4obj, ident.1 = "11", 
            min.diff.pct = 0.2, logfc.threshold = 0.5, 
            only.pos = T)
```

```{r}
#Reln 4th
FindMarkers(ENT.s4obj, ident.1 = "9", 
            min.diff.pct = 0.2, logfc.threshold = 0.5, 
            only.pos = T)
```

```{r}
#Cabindin
FindMarkers(ENT.s4obj, ident.1 = "4", 
            min.diff.pct = 0.2, logfc.threshold = 0.5, 
            only.pos = T)
```

## L2 Calbindin 
```{r}
VlnPlot(ENT.s4obj, features = "Calb1")
FeaturePlot(ENT.s4obj, features = "Calb1", label = T)
```

```{r}
FindMarkers(ENT.s4obj, ident.1 = "7", 
            min.diff.pct = 0.2, logfc.threshold = 0.5, 
            only.pos = T)
```


## excel workbook 
```{r}
workbook<- createWorkbook()
addWorksheet(workbook, sheetName = "HIP") # whole hippocampus
addWorksheet(workbook, sheetName = "ENT") # whole Entorhinal 
addWorksheet(workbook, sheetName = "NEO") # whole Neo cortex

addWorksheet(workbook, sheetName = "HIPd") # hippocampus dorsal 
addWorksheet(workbook, sheetName = "HIPv") # hippocampus ventral

addWorksheet(workbook, sheetName = "DGd") # DGd
addWorksheet(workbook, sheetName = "DGv") # DGv
addWorksheet(workbook, sheetName = "CA1v") # CA1v
addWorksheet(workbook, sheetName = "CA1d") # CA1d
addWorksheet(workbook, sheetName = "CA3d") # CA3d
addWorksheet(workbook, sheetName = "CA3v") # CA3v

addWorksheet(workbook, sheetName = "ENTm") # ENTm
addWorksheet(workbook, sheetName = "ENTl") # ENTl
```

```{r}
adultInfo<- function(diffResult){
  diffResult %>% 
    mutate(gene = rownames(diffResult))
}
```

```{r}
FindMarkers(ENT.s4obj, ident.1 = "L2 IT ENTm", 
            logfc.threshold = 0.5, min.diff.pct = 0.2,
            only.pos = T, group.by = "subclass_label")
```

```{r}
FindMarkers(ENT.s4obj, ident.1 = "L2 IT ENTl", 
            logfc.threshold = 0.5, min.diff.pct = 0.2, 
            only.pos = T, group.by = "subclass_label")
```

## select only InterNeuron 
```{r}
ENT.s4obj@meta.data %>%
  filter(grepl('ENT', subclass_label))-> ENT.ent.meta
ENT.s4obj@meta.data %>% 
  filter(grepl('CTX', subclass_label))-> ENT.ctx.meta
ENT.IT.meta<- rbind(ENT.ent.meta, ENT.ctx.meta)
```

```{r}
ENT.IT.s4obj<- ENT.s4obj[,rownames(ENT.IT.meta)]
```

```{r}
Idents(ENT.IT.s4obj)<- ENT.IT.s4obj@meta.data$subclass_label
DimPlot(ENT.IT.s4obj)
```

```{r}
Idents(ENT.IT.s4obj)<- ENT.IT.s4obj@meta.data$subclass_label
FeaturePlot(ENT.IT.s4obj, features = "Reln", label = T)+
  VlnPlot(ENT.IT.s4obj, features = "Reln",
          group.by = "subclass_label")
Idents(ENT.IT.s4obj)<- ENT.IT.s4obj@meta.data$region_label
```

```{r}
FeaturePlot(ENT.IT.s4obj, features = "Calb1", label = T)+
  VlnPlot(ENT.IT.s4obj, features = "Calb1")
```

```{r}
ENT.classes<- levels(ENT.IT.s4obj)
for(i in 1:length(levels(ENT.IT.s4obj))){
  print(DimPlot(ENT.IT.s4obj, 
                cells.highlight = 
                  WhichCells(ENT.IT.s4obj,
                             idents = ENT.classes[i]))+
          ggtitle(ENT.classes[i]))
}
```

```{r}
Idents(ENT.IT.s4obj)<- ENT.IT.s4obj@meta.data$region_label
DimPlot(ENT.IT.s4obj)
ENTm.IT.marker<- FindMarkers(ENT.IT.s4obj, ident.1 = "ENTm",
                             ident.2 = "ENTl", min.diff.pct = 0.2,
                             logfc.threshold = 0.5, only.pos = T)
ENTl.IT.marker<- FindMarkers(ENT.IT.s4obj, ident.1 = "ENTl",
                             ident.2 = "ENTm", min.diff.pct = 0.2,
                             logfc.threshold = 0.5, only.pos = T)
```

```{r}
ENTm.IT.marker
```

```{r}
ENTl.IT.marker
```

```{r}
FeaturePlot(ENT.IT.s4obj, features = "Reln")+
  VlnPlot(ENT.IT.s4obj, features = "Reln", group.by = "subclass_label")
FeaturePlot(ENT.IT.s4obj, features = "Calb1")+
  VlnPlot(ENT.IT.s4obj, features = "Calb1", group.by = "subclass_label")
FeaturePlot(ENT.IT.s4obj, features = "Satb2")+
  VlnPlot(ENT.IT.s4obj, features = "Satb2", group.by = "subclass_label")
FeaturePlot(ENT.IT.s4obj, features = "Tbr1")+
  VlnPlot(ENT.IT.s4obj, features = "Tbr1", group.by = "subclass_label")
FeaturePlot(ENT.IT.s4obj, features = "Rorb")+
  VlnPlot(ENT.IT.s4obj, features = "Rorb", group.by = "subclass_label")
```

```{r}
Idents(ENT.IT.s4obj)<- ENT.IT.s4obj@meta.data$subclass_label
ENT.IT.marker<- FindAllMarkers(ENT.IT.s4obj, logfc.threshold = 0.5,
                               min.diff.pct = 0.2, only.pos = T)
Idents(ENT.IT.s4obj)<- ENT.IT.s4obj@meta.data$region_label
```

```{r}
ENT.IT.marker %>%
  group_by(cluster) %>%
  top_n(n = 20, wt = avg_log2FC) 
```

```{r}
writeData(workbook, "HIP", adultInfo(HIPDiff02FC07))
writeData(workbook, "ENT", adultInfo(ENTDiff02FC05))
writeData(workbook, "NEO", adultInfo(NEODiff02FC07))

writeData(workbook, "HIPd", adultInfo(HIPDDiff02Fc06))
writeData(workbook, "HIPv", adultInfo(HIPVDiff02Fc06))

writeData(workbook, "DGd", adultInfo(HIPsubDVTop10[1:10,]))
writeData(workbook, "DGv", adultInfo(HIPsubDVTop10[11:20,]))
writeData(workbook, "CA1v", adultInfo(HIPsubDVTop10[21:30,]))
writeData(workbook, "CA1d", adultInfo(HIPsubDVTop10[31:40,]))
writeData(workbook, "CA3d", adultInfo(HIPsubDVTop10[41:50,]))
writeData(workbook, "CA3v", adultInfo(HIPsubDVTop10[51:60,]))

writeData(workbook, "ENTm", adultInfo(ENTMec))
writeData(workbook, "ENTl", adultInfo(ENTLec))
```

```{r}
saveWorkbook(workbook, 
             file = "region_info.xlsx", 
             overwrite = T)
```

